\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-09-25 docs/proposal/doc.tex
merge

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity. For this, implementations of PC and BCCD can be used. PC is a widely used algorithm and as such, many implementations already exist. An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university. The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset. This will result in a connectivity matrix which represents the effective connectivity. These results will  be evaluated by cross-subject comparison, to see whether the gained data is consistent. If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity. As PC is a state-of-the-art algorighm \cite{?}, and BCCD shows a good potential \cite{}, this way of determining effective connectivity may very well be the case.

>>>>

\section{Methods \& Strategy}
%Short general introduction to both methods
In this project, causal discovery algorithms will be applied to a dataset of functional and structural connectivity, in order to find effective connectivity. For this, implementations of PC and BCCD can be used. PC is a widely used algorithm and as such, many implementations already exist. An implementation of BCCD suitable for this project also exists at the department of Intelligent Systems of the Radboud university. The datasets of structural and functional connectivity are available, so the first step of this step will be to get the implementations for the algorithms working on the dataset. This will result in a connectivity matrix which represents the effective connectivity. These results will  be evaluated by cross-subject comparison, to see whether the gained data is consistent. If it is, then this algorithm is a potentially useful algorithm for determining effective connectivity. As PC is a state-of-the-art algorighm \cite{spirtes2000}, and BCCD shows a good potential \cite{claassen2012}, this way of determining effective connectivity may very well be the case.
